\vspace{-\baselineskip} Fast and scalable Gaussian process modeling with applications to astronomical time series \vspace{-3.2\baselineskip}

### 2017-03-25 paper/ms.tex
addressing comments from AGW

@@

\acknowledgments
It is a pleasure to thank
Megan Bedell,
Will Farr,
Sam Grunblatt,
David W.\ Hogg,
Dan Huber, and
Jake VanderPlas
for helpful discussions informing the ideas and code presented here.

>>>>

The structured kernel interpolation \citep[SKI/KISS-GP][]{Wilson:2015}
framework is another approximate method that can be used to scale GPs to large
datasets.
This method uses fast interpolation of the kernel into a space where Toeplitz
or Kronecker structure can be used to scale inference and prediction.
The SKI/KISS-GP framework can be applied to scale GP inference with a wide
range of kernels, but the computational cost will depend on the specific
dataset, model, and precision requirements for the approximation.
The SKI method has an impressive $\mathcal{O}(1)$ cost for test-time
predictions and it is interesting to consider how this could be applied to
\celeriteterm\ models.

@@

\acknowledgments
It is a pleasure to thank
Megan Bedell,
Ian Czekala,
Will Farr,
Sam Grunblatt,
David W.\ Hogg,
Dan Huber,
Dennis Stello,
Jake VanderPlas, and
Andrew Gordon Wilson
for helpful discussions informing the ideas and code presented here.
